Working title: Ecological network control

### 2018-05-10 paper/manuscript.Rmd
Make example direction networks

>>>>

```{r, fig.cap="Consider the 2", fig.height= 0.9, fig.width=3.5}
drake::loadd(en_direction)

# graph attributes
formatted_en_direction <- en_direction  %>%
  purrr::map(~ fancify_vertex_name(.)) %>%
  purrr::map(~ add_property(., element = "edge", attr_name = "color", 'TRUE ~ "black"')) %>%
  purrr::map(~ add_property(., element = "edge", attr_name = "label.color", 'TRUE ~ "black"')) %>%
  purrr::map(~ add_property(., element = "edge", attr_name = "label.font", 'TRUE ~ 2')) %>%
  purrr::map(~ add_property(., element = "vertex", attr_name = "color", "TRUE ~ 'white'")) %>%
  purrr::map(~ add_property(., element = "vertex", attr_name = "frame.color", "TRUE ~ 'black'")) %>%
  purrr::map(~ add_property(., element = "vertex", attr_name = "size", "TRUE ~ 55")) %>%
  purrr::map(~ add_property(., element = "vertex", attr_name = "label.cex", "TRUE ~ 1")) %>%
  purrr::map(~ add_property(., element = "vertex", attr_name = "label.color", "TRUE ~ 'black'"))
formatted_en_direction[[1]] %<>%
  igraph::set_edge_attr("label", value = igraph::E(.)$weight)
formatted_en_direction[[2]] %<>%
  igraph::set_edge_attr("label", value = "")

if(out_pdf) pdf("test.pdf", width = 3.5, height = 0.9)

# graph layout
layout(matrix(c(1,5,2,
                3,5,4), nrow = 2, ncol = 3, byrow = TRUE),
       heights= c(0.35, 1), 
       widths = c(1, 0.05, 1))
par(mar=c(0.0,0,0,0), bg = "white", xpd = NA)

# 1
plot.new()
text(0.5,0.25, "visitation network", adj = c(0.5,0), font = 2, cex = 0.9)

# 2
plot.new()
text(0.5,0.25, "direction of control", adj = c(0.5,0), font = 2, cex = 0.9)

# network layout
l <- matrix(c(1,0,
              2,0,
              3,0,
              1.5, 1,
              2.5, 1), nrow = 5, ncol = 2, byrow = T)

# 3-4
for(i in 1:length(formatted_en_direction)){
   set.seed(3)
  types <- igraph::V(formatted_en_direction[[i]])$type ==
    dplyr::first(igraph::V(formatted_en_direction[[i]])$type)
  l <- l %>%
    rescale_layout(xlim = c(-1, 1) * 1.75, ylim = c(-0.6, 0.7))
  plot_examples(formatted_en_direction[[i]], 
                layout = l, rescale = F, frame = F, margin = rep(0, 4), 
                edge.arrow.size = 0.4,
                edge.label.family = "sans", 
                vertex.label.family = "sans")
}

# 5
plot.new()
segments(0,0,0,1, lty = 2, lwd = 0.5)
